Job mobility and earnings growth: diffrerent markets, different outcomes.

### 2018-10-16 draft.Rmd
Update draft.Rmd

Our approach is a parallel case study using two longitudinal panels, the British Household Panel Survey, and the German Socio-Economic Panel. It has three strengths. First, we include internal mobility (promotions) in our analysis, which is often ignored. Second, we take a longitudinal approach to estimating the effects of changing jobs. In this way, we avoid the conclusions of authors who compare movers to non-movers; instead we are able to observe the effects of moving from one position to another. Third, we compare and contrast the effects of moving in two different institutional settings, where authors typically rely on one. This approach allows us to compare and contrast the importance of local institutions on job mobility.

@@

The article helps to understand processes of inequality, where workers best placed to pursue promotion, are those most likely to see higher earnings later in their career. The decline of career ladders and the “death” of careers (Cappelli, 1999) has prompted some to embrace flexible and mobile markets (Arthur and Rousseau, 2001, Tolbert, 1996). The narrative suggests that workers are able to gain through quits what was on offer through promotion. Our findings suggest that promotion and quits are distinctly different mechanisms for improving earnings. Although mobility ay be a necessary strategy to place oneself near an internal career lader, access to promotions may be understood as an important key to understanding inequality in both countries.

>>>>

Our approach is a parallel case study using two longitudinal panels, the British Household Panel Survey, and the German Socio-Economic Panel. It has three strengths. First, we consider internal mobility (promotions) in our analysis, which are often ignored. Second, we take a longitudinal approach to estimating the effects of changing jobs. In this way, we avoid the conclusions of authors who compare movers to non-movers; instead we are able to observe the effects of moving from one position to another. Third, we compare the effects of moving in two different institutional settings, where authors typically rely on one. Thus, the article allows us to compare and contrast the importance of local institutions on job mobility.

@@

The article helps to understand processes of inequality; workers who are best placed to pursue promotion, are those most likely to see earnings growth. In another sense, those workers who are best placed to receive promotions, are thus more likely to ber rewarded. The decline of career ladders and the “death” of careers (Cappelli, 1999) has prompted some to embrace flexible and mobile markets (Arthur and Rousseau, 2001, Tolbert, 1996). This narrative suggests that workers are able to gain through quits what was on offer through promotions. Our findings suggest that promotion and quits are distinctly different mechanisms for improving earnings. Although mobility may be a strategy to place oneself near internal career laders, access to promotions can be understood as an important mechanism to understanding inequality in both countries.
